Paper TITLE

### 2016-08-06 code/Paper.Rmd
minor grammar changes

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  labs(title = "Relationship between Household \nIncome and Burden", 
       y = "Household Income ($)", x = "Year", color = "Burden") +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()

>>>>

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  labs(title = "Figure : Relationship between Household \nIncome and Burden", 
       y = "Household Income ($)", x = "Year", color = "Burden") +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()
